Learning constraints in spreadsheets and tabular data

### 2016-06-07 Paper/ECAI/tabular.tex
shortened the paper

Consider Figure \ref{fig:autocompletion_example} containing two tables.
Learning on a snapshot that does not contain line 17, we find constraints $\ecsumif{\range{T_2}{\rangeall}{2}}{\range{T_1}{\rangeall}{2}}{\range{T_2}{\rangeall}{1}}{\range{T_1}{\rangeall}{3}}$ and $\ecsumif{\range{T_2}{\rangeall}{3}}{\range{T_1}{\rangeall}{2}}{\range{T_2}{\rangeall}{1}}{\range{T_1}{\rangeall}{4}}$.
The new data $\Delta D$ consists of the new value \textit{West} on line 17.
Therefore, vector~$\range{T_2}{:}{1}$ is changed and vectors~$\range{T_2}{:}{2}$, $\range{T_2}{:}{3}$ have become incomplete.
The \textit{SUMIF} constraints have enough input to fill the incomplete vectors and predict the values in the last row: $\range{T_2}{4}{2} = 1547$ and $\range{T_2}{4}{3} = 428128$.

@@

\subsection{Error detection}
\begin{figure*}[thb]
\begin{subfigure}{.70\textwidth}
  \begin{center}
    \includegraphics[width=\textwidth]{figures/fbi_figure_highlighted.png}
  \end{center}
  \caption{Real world tabular constraint reconstruction: FBI crime statistics}
  \label{fig:fbi}
\end{subfigure}
\hfill
\begin{subfigure}{.29\textwidth}
\begin{center}
    \includegraphics[width=\textwidth]{figures/autocompletion_example.png}
  \end{center}
  \caption{\sergey{Samuel, Tias have a look at it, should be corrected and extended, like with groups indications and formulas?}}
  \label{fig:autocompletion_example}
\end{subfigure}
\end{figure*}

>>>>

% Consider Figure \ref{fig:autocompletion_example} containing two tables.
% Learning on a snapshot that does not contain line 17, we find constraints $\ecsumif{\range{T_2}{\rangeall}{2}}{\range{T_1}{\rangeall}{2}}{\range{T_2}{\rangeall}{1}}{\range{T_1}{\rangeall}{3}}$ and $\ecsumif{\range{T_2}{\rangeall}{3}}{\range{T_1}{\rangeall}{2}}{\range{T_2}{\rangeall}{1}}{\range{T_1}{\rangeall}{4}}$.
% The new data $\Delta D$ consists of the new value \textit{West} on line 17.
% Therefore, vector~$\range{T_2}{:}{1}$ is changed and vectors~$\range{T_2}{:}{2}$, $\range{T_2}{:}{3}$ have become incomplete.
% The \textit{SUMIF} constraints have enough input to fill the incomplete vectors and predict the values in the last row: $\range{T_2}{4}{2} = 1547$ and $\range{T_2}{4}{3} = 428128$.

@@

\subsection{Error detection}
\begin{figure}[thb]
%\begin{subfigure}{.70\textwidth}
  \begin{center}
    \includegraphics[width=\linewidth]{figures/fbi_figure_highlighted.png}
  \end{center}
  \caption{Real world tabular constraint reconstruction: FBI crime statistics}
  \label{fig:fbi}
%\end{subfigure}
% \hfill
% \begin{subfigure}{.29\textwidth}
% \begin{center}
%     \includegraphics[width=\textwidth]{figures/autocompletion_example.png}
%   \end{center}
%   \caption{\sergey{Samuel, Tias have a look at it, should be corrected and extended, like with groups indications and formulas?}}
%   \label{fig:autocompletion_example}
% \end{subfigure}
\end{figure}
